\documentstyle[11pt]{article}

\oddsidemargin=.25in
\evensidemargin=.25in
\textwidth=6in
\topmargin=0in
\textheight=9in

\parindent=0in
\pagestyle{empty}

\input{lauracode}

\begin{document}

Dear ApSys Travel Grant Committee Members,
\vs
%\gotable{0}{1}{rlp{.1in}rl}
%{\bf Instructor:} & Laura Taalman 		 
%   && {\bf Office:}   & 020 Math/Physics \\
%{\bf Telephone:}  & 660-2829 (W), 220-1359 (H) 
%   && {\bf E-mail:}   & taal@math.duke.edu \\
%\stoptable

I am a first year doctoral student in the Electrical Engineering 
department of Korea Advanced Institute of Science \& Technology (KAIST).
I work with Prof. KyoungSoo Park in the Networked \& Distributed Systems
Computing Lab (NDSL) where I am primarily involved in networked systems
security research. My past projects have focused on developing robust 
systems for preventing malicious traffic spread by botnets. This has 
yielded in workshop and conference publications including one 
in ApSys 2010. More recently I have been working on two projects, one of 
which employs trusted computing techniques to identify human generated 
traffic in the Internet. The other focuses on developing a novel 
networked system architecture for high-speed session-layer I/O.
Despite doing research for the past four years I have never had the 
experience of attending a systems conference/workshop where I can share 
my research ideas and meet my peers \& experts.
\vs

Participating in the forthcoming ApSys 2011 will not only be extremely 
relevant to my research interests and for networking within the academic 
community but will also allow me (on behalf of the project team) to 
receive feedback on my current projects from the experts in the area.
\vs

I hope for a favorable decision.
\vs

Sincerely,
\vs

Muhammad Asim Jamshed \\
ajamshed@ndsl.kaist.edu \\
http://www.ndsl.kaist.edu/$\sim$ajamshed \\
\end{document}
